%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/, https://github.com/treyhunner/resume)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref}

\name{Edward Pearce} % Your name
\address{Email: \href{edwardm.pearce@gmail.com}{edwardm.pearce@gmail.com} \\ \href{https://www.linkedin.com/in/edwardm-pearce/}{linkedin.com/in/edwardm-pearce}} % Contact details line 1 (e.g. phone and email)
\address{Website: \href{https://edwardmpearce.github.io}{edwardmpearce.github.io} \\ \href{https://github.com/edwardmpearce}{github.com/edwardmpearce}} % Contact details line 2 (e.g. address)

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf The University of Sheffield, PhD in Mathematics} \hfill {\em October 2016 - March 2021} \\ 
\emph{Generalized core-quotient decomposition for partitions and applications in algebraic geometry} \\
{\bf University of Warwick, MMath Master of Mathematics} \hfill {\em October 2012 - July 2016} \\
First Class Honours. 92.8\% overall; top 2\% in a class of $\approx$ 300.

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}
	
\begin{rSubsection}{Liberty Specialty Markets}{June 2022 - Present}{Pricing Analyst}{London, UK}
	\item Delivering actuarial pricing and portfolio analytics across specialty and commercial insurance and reinsurance lines of business in multiple continents, including European PI, D\&O, and Marine Hull
	\item Full-stack web development of reinsurance contract pricing application using simulated loss distributions
	\item Leading digital transformation group project translating Excel rating tools into Python/React web applications for underwriters and actuaries; organising and running Agile retrospective sessions
	\item Conducting comprehensive peer review for predictive modelling projects, covering documentation practices, data quality, statistical modelling assumptions, and technical code review; Creating evaluation framework including checkpoints, required outputs, and review checklists for each stage of model R\&D
	\item Running training sessions on software development best practices, unit testing, and version control; coaching junior team members in programming, and project line management for graduate rotation
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Munich Re (GrovesJohnWestrup Private Clients)}{March 2021 - June 2022}{Pricing Data Scientist}{London, UK}
	% \item GrovesJohnWestrup Private Clients is a Munich Re company providing a leading technology solution to the HNW insurance market
	\item Building and managing the company's data analysis and visualization infrastructure end-to-end using Python, R, SQL, Power BI, including data engineering, API enrichment, and dashboard production for daily monitoring of sales funnel, claims, premium adequacy, broker performance, AML compliance, etc.
	\item Collaborating across functions to understand business requirements and create automated tools saving hours per week on BAU processes (7.5\% of one team's time) and enabling more data-driven approach
	\item Developing, testing, and deploying machine learning models to enhance pricing and portfolio management in home insurance and pet insurance contexts
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Health Data Insight}{July 2019 - September 2019}{Cancer Data Analyst}{Cambridge, UK}
\item Building a framework to analyse synthetic datasets of patient tumour records
\item Using Python and SQL for data extraction, automating statistical tests, visualization
\item Presenting results to HDI board members and Public Health England stakeholders
\item Chairing Analysts East team meeting; organising social events (group meals, punting)
\end{rSubsection}

%------------------------------------------------

% \begin{rSubsection}{STFC AI\&ML Summer School UCL}{July 2018}{}{}
% \item Lectures from ASI Data Science on machine learning algorithms in theory and practice
% \item Practical labs using cloud computing with Intel (Devcloud), Amazon (Web Services), Nvidia
% \item Case studies on applications in industry and physics from Dell, Mellanox, LIGO, SKA
% \item Poster session presenting; volunteering for an outreach event to teach secondary school children about decision trees and deep learning using LHC data.
% \end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{TAS Services Ltd}{July 2016 - September 2016}{Research Analyst}{Hong Kong}
\item Using Python for web scraping, data analysis and interfacing with SQL and mongoDB
\item Automating data comparison across multiple sources for accurate data management
\item Linking databases and preparing data for statistical modelling to inform investment strategies
\item Discovering a new culture through international work experience
\end{rSubsection}

%------------------------------------------------

% \begin{rSubsection}{Warwick Maths Society}{February 2014 - April 2016}{President (2015/6) \& Sponsorship Officer (2014/5)}{University of Warwick}
% \item Managing a team of 15 exec members, chairing meetings, and organising events of varying sizes for our 900-strong membership, including external trips, summer barbecue
% \item Securing two new sponsors for the society, increasing sponsorship funds by 100\%
% \item Presenting at the Warwick Imperial undergraduate conference on my URSS summer research project.
% \item Delivering a revision lecture on linear algebra to over 200 of my peers
% \end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TEACHING SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Teaching Experience}
	
	{\bf Graduate Teaching Assistant} \hfill October 2016 - December 2020 \\
	{\em University of Sheffield:} Face-to-face and online teaching experience leading tutorials on topics including Core Mathematics, Engineering Mathematics, Scientific Computing, and Statistical Data Science. \\
	Programming labs and mathematics tutorials with class sizes ranging from 15-40 students.
	
	{\bf Supervisor} \hfill October 2015 - July 2016 \\
	{\em University of Warwick:} Small group teacher for 2x5 1st year mathematics students plus marking. \\
	% Modules covered: MA132 Foundations, MA133 Differential Equations, MA136 Introduction to Abstract Algebra, MA131 Analysis I and II, MA106 Linear Algebra, MA134 Geometry and Motion.
	
	% {\bf Poster presentations} \\
	% {\em Hilbert schemes of Cyclic Quotient Surfaces},
	% Géométrie Algébrique en Liberté XXVI (Uni. of Strasbourg, June 2018), STFC Summer School in AI\&ML (UCL, July 2018) \\
	% {\em Fabulous Fractions and Musical Scales}, 
	% Faculty of Science Graduate Student Showcase (Uni. of Sheffield, April 2018)
	
\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}

{\em Physics Simulation: n-body system} \hfill Spring Semester 2020 \\
Extracurricular course assignment for COM4521 Parallel Programming with GPUs. Comparing performance of serial and parallel programming techniques using C, OpenMP, and CUDA.\\
Source code: \href{https://github.com/edwardmpearce/COM4521}{https://github.com/edwardmpearce/COM4521}

{\em PyParti: Python for Partitions} \hfill July 2020 \\
Python/SageMath package for integer partitions, combinatorics calculations and visualization. \\
Automated testing with GitHub Actions workflow.
\href{https://mybinder.org/v2/gh/edwardmpearce/pyparti/master}{Cloud-hosted notebooks} with Docker and Binder.
Source code: \href{https://github.com/edwardmpearce/pyparti}{https://github.com/edwardmpearce/pyparti}

{\em Simulacrum Test Suite} \hfill July 2019 - September 2019 \\
Software for calculation and visualisation of statistical tests comparing a synthetic dataset with its training set, written using Python, Oracle SQL.
Presented at \href{https://healthdatainsight.org.uk/hdi-symposium-2019/}{HDI Symposium} (Cambridge, Nov. 2019)

{\em Personal Website} \hfill Spring 2019 - Present \\
\href{https://edwardmpearce.github.io/}{Website} for online resume, teaching material, mathematical puzzles, web development practice.\\
Written with Hugo (Go-based web framework). Continuous Integration with Travis CI.

{\em Partitions Lab} \hfill Spring Semester 2019 \\
\href{https://edwardmpearce.github.io/tutorial-partitions/}{Tutorial website} about integer partitions, with interactive code cells using SageMath computer mathematics software. 
Written with Hugo, LaTeX, TikZ, HTML, JavaScript.

{\em Artificial Intelligence and Earth Observation for the Prediction of Malaria Outbreak Risk} \hfill May 2019 \\
Data science project for isardSAT using satellite data on soil moisture and land temperature. \\
Source code: \href{https://github.com/edwardmpearce/cardiff-study-group-ai-in-healthcare}{https://github.com/edwardmpearce/cardiff-study-group-ai-in-healthcare}\\
Presented at Innovate UK AI in Health \& Care Study Group with Industry at Uni. of Cardiff.

{\em Sporadic Finite Subgroups of SL(3,C) and their McKay Quivers} \hfill July 2015 - September 2015 \\
Funded by grant through the Undergraduate Research Scholarship Scheme, supervised by Professor Miles Reid, University of Warwick. 
Source code: \href{https://github.com/edwardmpearce/urss-project}{https://github.com/edwardmpearce/urss-project} \\
Presented at \href{https://warwick.ac.uk/fac/sci/maths/research/events/2015-16/nonsymposium/wimp/}{Warwick Imperial Autumn Meeting} (Uni. of Warwick, Nov. 2015)

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Additional Skills}
	
	\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
		Computer Languages & Python (PyData stack: pandas, scikit-learn, matplotlib, Plotly), \\
		& C (OpenMP, CUDA), R, Power BI (Power Query M, DAX), \\
		& Java, Matlab, Mathematica, Magma, Excel VBA \\
		Databases & MySQL, Oracle SQL, mongoDB, MSSQL Server, T-SQL, Snowflake \\
		Tools and Frameworks & LaTeX, git, bash, Hugo, Flask, React JS, Docker \\
		Languages & English (native), Mandarin Chinese (Limited working proficiency) \smallskip \\
		Interests & Indoor Bouldering, Yoga, Urban Cycling, CS50x, \href{https://github.com/edwardmpearce/adventofcode}{Advent of Code}
	\end{tabular}
	
\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
